---
title: "Plotting data corresponding to MET and EEA1 colocalization"
author: "José Liboy Lugo"
date: "2026-06-13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document presents the analysis of colocalization data between MET and EEA1 markers from fluorescent microscopy images.
After image processing on python script met_coloc_analysis.py, the results are visualized in this document.


## Loading the data

Data was previously saved in a CSV files 

```{r loading data}
library(readr)
library(dplyr)
library(purrr)

path_folder <- '/Users/joselito/Desktop/Carla_IF_data/rdata/'
files <- list.files(path_folder, pattern = "\\.csv$", full.names = TRUE)

data_list <- map(files, read_csv) # Read all CSV files into a list
merged_data <- reduce(data_list, rbind) # Merge all data frames
print(merged_data)
#
```

## Plotting MET and EEA1 colocalization data


```{r plotting, echo=FALSE}
library(ggplot2)
library(plotrix)

plot_coloc = merged_data %>%
  group_by(Treatment, Time) %>%
  summarise(average_coloc = mean(Colocalization_fraction),
            sem_coloc = std.error(Colocalization_fraction))

plot_coloc$Time <- as.factor(plot_coloc$Time)
plot_coloc$Treatment <- factor(plot_coloc$Treatment, levels = c("No Ligand", "HGF only", "HGF + SNRP"))



coloc_plot <- ggplot(data = plot_coloc, aes(x = Time, y = average_coloc, fill = Treatment, group = Treatment)) + 
geom_col(linewidth = 0.75, position = position_dodge2(width = 0.9, preserve = "single")) + 
geom_errorbar(data = plot_coloc, width = 0.9, aes(ymin = average_coloc - sem_coloc, 
                                       ymax = average_coloc + sem_coloc), 
                position = position_dodge2(width = 0.9, padding = 0.8, preserve = "single")) + 
  ylim(0,0.75) + theme_classic() + 
  labs(x = 'time (min)', y = 'Mean fraction of MET colocalizing with endosomes')

print(coloc_plot)

ggsave("./coloc_plot.svg", plot = coloc_plot, width = 5, height = 5, units = "in")
dev.off()
```

## Calculating statistical significance via t-tests 

```{r t-test}
# Perform a t-test to compare the colocalization fractions between different treatments
t_test_15min <- t.test(Colocalization_fraction ~ Treatment, data = merged_data, subset = Time == 15)
print(t_test_15min)

t_test_30min <- t.test(Colocalization_fraction ~ Treatment, data = merged_data, subset = Time == 30)
print(t_test_30min)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
